Reanalysis Step 2b: Multiple Imputation Outcome Diagnostics

### 2025-08-29 reanalysis-2b-imputation_diagnostics.qmd
enhance

```{r calculate-changes}
# Function to calculate change scores for a single imputed dataset
calculate_change_scores <- function(imp_data, original_data) {
  imp_data |>
    mutate(
      # Add imputation status from original data
      outcome_was_imputed = original_data$outcome_was_imputed,
      had_intermediate = original_data$had_intermediate,
      imputation_group = original_data$imputation_group,

@@

```{r baseline-predictors}
# Merge baseline characteristics with change scores
analysis_df <- changes_df |>
  left_join(df_original |> select(CCI, DCSI, age, baseline_VA_logMAR), 
            by = c("baseline_VA_logMAR"))

>>>>

```{r calculate-changes}
# Add row identifier to original data for proper merging
df_original <- df_original |>
  mutate(row_id = row_number())

# Function to calculate change scores for a single imputed dataset
calculate_change_scores <- function(imp_data, original_data) {
  imp_data |>
    mutate(
      row_id = row_number(),
      # Add imputation status from original data
      outcome_was_imputed = original_data$outcome_was_imputed,
      had_intermediate = original_data$had_intermediate,
      imputation_group = original_data$imputation_group,

@@

```{r baseline-predictors}
# Merge baseline characteristics with change scores using row_id (already added earlier)
analysis_df <- changes_df |>
  left_join(df_original |> select(row_id, CCI, DCSI, age), 
            by = "row_id")
